Poseidon Adventure

### 2019-10-01 SardinesHakeatlantisom2SStest.Rmd
update index and current run status

#Get correct number of length bins
# stocksynthesis.data$N_lbins <- length(length_bins)

@@

## Coming up with dynamic life history parameters

@@

```{r runSS, eval=FALSE}
#Run stock synthesis model 
# default runs with admb_options = "-noest"
#run_stocksynthesis(species = species, model_dir = model_dir, show_output = TRUE)

>>>>

#Get correct number of length bins
stocksynthesis.data$N_lbins <- length(length_bins)

@@

## Coming up with dynamic life history parameters (partial from Christine)

@@

```{r runSS}
#Run stock synthesis model 
# default runs with admb_options = "-noest"
#run_stocksynthesis(species = species, model_dir = model_dir, show_output = TRUE)

### 2019-10-01 docs/index.Rmd
update index and current run status

>>>>

The below generates a readable dat file for input into SS3 for sardines. The control file and biological parameters still need hand modification, but SS3 now runs.

<a href="https://sgaichas.github.io/poseidon-dev/SardinesHakeatlantisom2SStest.html" target="_blank">Sardines in the CalCurrent run with F, rec dev, and climate scenario, all true and SS data, October 1, 2019</a>
